Untitled

### 2020-08-05 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary material (new order)

__Table S3.__ Seed:ovule ratio (%) of the different reproductive biology treatments.

__Table S4.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

@@

__Figure S1__. Species reproductive biology.

__Figure S2__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

__Figure S3__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.

__Figure S4__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.

__Figure S5__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.

__Figure S6__. Unipartite bidirectional network with asymmetrical effect.

__Figure S7__. Correlation matrix for all the different traits.

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species. The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S1** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow). The coloured dots, represent the different values of seed:ovule ratio for each treatment."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig. S2** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment). For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma. For each pair of species on the x-axis, the first species is the recipient species, and the second, the donor species."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig. S3** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae. These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments. We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these treatments. The proportion of conspecific and heterospecific pollen are shown in grey and light blue respectively. For each pair of species on the y-axis, the first species is the pollen recipient and the second the pollen donor. The vertical black line represents 50% pollen of both donor and recipient."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig. S4** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted. We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments. Finally, we grouped by family these treatments in order to see general tendencies across families as pollen donor and as pollen recipient. Pollen ratios were considered as the number of conspecific or heterospecific pollen grains divided by the total number of pollen grains per stigma. On the y-axis, the first family on each pair of plant families is the recipient one, and the second, the family of the donor. The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S5** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons). These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen). Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig. S6** Unipartite bidirectional network with asymmetrical effect. The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species. All the arrow heads point to the recipient species of the reciprocal interaction. Lines of species that did not have a negative impact are not represented. The different nodes and the effect of the donor species on the recipient species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size. Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig. S7** Graphical representation of the correlation matrix of all the traits measured. Positive correlations are displayed in blue and negative in red. The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
#install.packages("corrplot")
library(corrplot)
setwd("~/R_projects/Hp_pollen_experiment")
#Example
#I'm going to try to show our traits on this way
#M <- cor(mtcars)
#corrplot(M, method = "circle")
#We can kill two birds with one stone, showing the correlation and all the traits
traits_all <- read.csv("Data/Csv/traits_all.csv")
si_index <- readRDS("Data/RData/si_index.RData")
traits_all$si_index <- si_index
traits_all=traits_all[,-c(1,2)]
traits_all=traits_all[,-c(1,7,11)]
#Change order of ovary width length I rename below in row and colname
a<-traits_all[,11]
b<-traits_all[,12]
traits_all[,11] <-b
traits_all[,12]<- a
traits_all<- cor(traits_all)

@@

>>>>

__Table S3.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

__Table S4.__ Seed:ovule ratio (%) of the different reproductive biology treatments.

@@

__Figure S1__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

__Figure S2__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.

__Figure S3__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.

__Figure S4__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.

__Figure S5__. Unipartite bidirectional network with asymmetrical effect.

__Figure S6__. Correlation matrix for all the different traits.

__Figure S7__. Species reproductive biology.

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species. The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig. S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment). For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma. For each pair of species on the x-axis, the first species is the recipient species, and the second, the donor species."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig. S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae. These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments. We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these treatments. The proportion of conspecific and heterospecific pollen are shown in grey and light blue respectively. For each pair of species on the y-axis, the first species is the pollen recipient and the second the pollen donor. The vertical black line represents 50% pollen of both donor and recipient."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig. S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted. We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments. Finally, we grouped by family these treatments in order to see general tendencies across families as pollen donor and as pollen recipient. Pollen ratios were considered as the number of conspecific or heterospecific pollen grains divided by the total number of pollen grains per stigma. On the y-axis, the first family on each pair of plant families is the recipient one, and the second, the family of the donor. The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S4** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons). These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen). Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig. S5** Unipartite bidirectional network with asymmetrical effect. The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species. All the arrow heads point to the recipient species of the reciprocal interaction. Lines of species that did not have a negative impact are not represented. The different nodes and the effect of the donor species on the recipient species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size. Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig. S6** Graphical representation of the correlation matrix of all the traits measured. Positive correlations are displayed in blue and negative in red. The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
#install.packages("corrplot")
library(corrplot)
setwd("~/R_projects/Hp_pollen_experiment")
#Example
#I'm going to try to show our traits on this way
#M <- cor(mtcars)
#corrplot(M, method = "circle")
#We can kill two birds with one stone, showing the correlation and all the traits
traits_all <- read.csv("Data/Csv/traits_all.csv")
si_index <- readRDS("Data/RData/si_index.RData")
traits_all$si_index <- si_index
traits_all=traits_all[,-c(1,2)]
traits_all=traits_all[,-c(1,7,11)]
#Change order of ovary width length I rename below in row and colname
a<-traits_all[,11]
b<-traits_all[,12]
traits_all[,11] <-b
traits_all[,12]<- a
traits_all<- cor(traits_all)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig. S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow). The coloured dots, represent the different values of seed:ovule ratio for each treatment."}
